Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
add info on fitts' law

This suggests that the icon on the top left-hand corner ---which happens to be the directions screen in this app--- is the most important. I would have to agree that getting directions is very important functionality, so it seems as if the app is complying to the guidelines. However, a couple of test subjects tried to click on the icon second from the right on the bottom for directions. It is possible that this guideline of important functionality being `elevated' may not be intuitive to all users.

@@

\medskip
\medskip

@@

The lack of standard iOS icons in the Google Maps app may or may not explain some of the efficiency issues as well as some errors that occurred with the tasks on the mobile Google Maps app. The guideline of important functionality being towards the upper-left corner of the screen may or may not explain some of the efficiency issues as well as errors that occurred with the tasks on the mobile Apple Maps app.

@@

must recognize that there are limitations to our studies-- didn't test all five metrics; less data for Apple maps; Apple maps is newer; etc.
Judgment call -- google maps with data that we have now.
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

This suggests that the icon on the top left-hand corner ---which happens to be the directions screen in the Apple Maps app--- is the most important. I would have to agree that getting directions is a very important functionality. Thus, it seems as if the app is complying to the guidelines. However, a couple of test subjects tried to click on the icon second from the right on the bottom for directions. It is possible that this guideline of important functionality being `elevated' may not be intuitive to all users.

@@

@@

The Apple Maps mobile application certainly complies to the guideline of placing important functionality toward the upper-left corner of the screen. Although this is a guideline provided by Apple, it is not entirely clear whether or not this is the best placement for important functionality. The top corner opposite to the hand the user holds the phone with requires a little extra effort and stretching for many hands. This adds an additional variable in an equation known as Fitts' Law\cite{Fitts}, which is indicative of an increase in the movement time. The motion between two targets is no longer a fluid, resistance-free motion. It is possible that, even though it complies with Apple guidelines, the placement of the directions button caused errors that could be preveted by a different placement. In a future study, it would be noteworthy to deduce what placement is optimal for efficiency, error prevention, and satisfaction.

@@

must recognize that there are limitations to our studies-- didn't test all five metrics; less data for Apple maps; Apple maps is newer; etc.
Judgment call -- google maps with data that we have now.
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Fitts}Fitts, Paul M. ``The information capacity of the human motor system in controlling the amplitude of movement" \emph{Journal of Experimental Psychology}, June 1954.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
